Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-28 200_code/final_code.qmd
structural changes

```{r}
ggplot(completed_data, aes(x=Region_fac, y = Life.Expectancy)) +
  geom_boxplot() +
  labs(x = "U.S. Region", y='Average Life Expectancy (Yrs)', color='U.S. Region', title='County Average Life Expectancy Distribution, Stratified by Region') +
  #scale_color_hue(labels = c("Inadequate", "Adequate"))+ 
  theme(plot.margin = margin(t = 20, r = 30, b = 20, l = 10),
axis.title.x = element_text(size = 8),
axis.title.y = element_text(size = 8),
title=element_text(size=9))
```

>>>>

```{r}
ggplot(completed_data, aes(x=Region_fac, y = Life.Expectancy)) +
  geom_boxplot() +
  labs(x = "U.S. Region", y='Average Life Expectancy (Years)', color='U.S. Region', title='County Average Life Expectancy Distribution, Stratified by Region') +
  #scale_color_hue(labels = c("Inadequate", "Adequate"))+ 
  theme(plot.margin = margin(t = 20, r = 30, b = 20, l = 10),
axis.title.x = element_text(size = 9),
axis.title.y = element_text(size = 9),
title=element_text(size=9))
```

### 2024-12-28 paper_files/paper.tex
structural changes

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\usepackage{float}
\floatplacement{table}{H}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

This study examines the relationships between socioeconomic, health, and
education indicators in U.S. counties using data from the American
Community Survey, the USDA Food Environment Atlas, Small Area Income and
Poverty Estimates, and other sources.We analyze how factors such as
residential segregation, health insurance coverage, access to healthy
foods, and region influence life expectancy, and how residential
segregation and region affect school funding adequacy. Our findings
reveal that life expectancy is influenced by residential segregation and
uninsured rates, though these effects are minor compared to the more
substantial influence of household income and regional differences. Life
expectancy averages are highest in the Northeast, followed by the
Midwest, West, and South. Region also plays the most significant role
out of all included variables in determining the likelihood of school
funding adequacy, with schools in the Northeast and Midwest being far
more likely to receive adequate funding than those in the South. Other
factors, such as residential segregation, property taxes, and household
income, show statistically significant but smaller effects. These
results highlight the complex interplay between socioeconomic variables
and geographic location in shaping public well-being. By identifying key
disparities in health and education, this study underscores the
importance of equitable resource allocation and targeted policies to
address regional and socioeconomic inequalities.

@@

Life expectancy and school funding are important indicators of public
well-being because they capture fundamental aspects of health,
education, and social equity that are essential for the development of
individuals and communities. Life expectancy is an important health
indicator that reflects not only the overall health of a society, but
also its stability, economic resilience, and levels of inequality. While
access to quality healthcare and nutritious foods are drivers of
well-being, where you live and the nature of the community you live in
likely also have an influence on health outcomes such as life
expectancy. According to ``The Root Causes of Health Inequity -
Communities in Action'' report from the National Institutes of Health,
we can infer that differences in life expectancy between regions and
socioeconomic groups often reveal systemic inequalities, with
marginalized communities experiencing shorter life spans due to limited
access to health care, healthy living environments, and economic
opportunities.\textsuperscript{1}~When it comes to educational
indicators, adequately funded schools ensure that students have equal
access to learning opportunities, serving as a crucial investment in
social mobility. The Stanford Center for Opportunity Policy in Education
highlights that ``the unequal allocation and inadequate levels of
resources in schools and communities {[}are{]} at the heart of many gaps
in student opportunity.''\textsuperscript{2} This emphasizes the
importance of equitable and adequate school funding in closing
opportunity gaps and empowering students from disadvantaged backgrounds
to achieve academic and economic success. By better understanding the
correlates of school funding adequacy, we can take a major step towards
implementing policy that targets the areas and communities most affected
by this issue.

@@

Variables of interest were selected a priori based on their perceived
relevance to the two outcomes we wanted to better understand: average
life expectancy and school funding adequacy. While nutrition and access
to quality healthcare are inherently linked to general wellbeing, it is
worthwhile to assess how influential the environmental and financial
aspects of these factors are on our tangible outcome. Therefore, we
selected two key predictors for our life expectancy model: the
percentage of the population with limited access to healthy foods and
the percentage of uninsured adults in a county. The former is defined by
the US Department of Agriculture as ``the percentage of the {[}county{]}
population that is low-income and does not live close to a grocery
store'', where ``close'' is defined differently for rural and nonrural
areas.\textsuperscript{6} The latter variable represents the percentage
of adults in a county younger than 65 who lack health insurance. We also
were interested in seeing how residential segregation would impact life
expectancy among these predictors, given existing studies on the
negative health effects of segregation, and whether this relationship
would exhibit any variations across different regions. This is why we
chose to include residential segregation index values as a predictor.
The residential segregation index, used by the County Health Rankings \&
Roadmaps program, measures how evenly two groups, such as Black and
white residents, are distributed across geographic areas, with values
ranging from 0 (complete integration) to 100 (complete
segregation).\textsuperscript{7}~

@@

\subsubsection{\texorpdfstring{\emph{Data
Overview}}{Data Overview}}\label{data-overview}

@@

Based on the multiple linear regression results, residential
segregation, percentage of uninsured adults, region, and median
household income all showed statistically significant effects on life
expectancy. Specifically, for every \$10,000 increase in median
household income, life expectancy increases by 1.25 years on average. In
addition, the impact of region on life expectancy was substantial: life
expectancy is on average 1.96 years higher in the West region compared
to the South, 2.92 years higher in the Northeast compared to the South,
and 1.92 years higher in the Midwest compared to the South, even when
controlling for income, uninsured population, and racial diversity. This
suggests, income as a factor withstanding, the differing quality of and
access to healthcare and public services found in each region can have a
significant impact on life expectancy.

Surprisingly, holding all other variables constant, for every 1 unit
increase in percentage of uninsured adults in a county, a county's
average life expectancy increases by 0.032 years. While statistically
significant, many studies covering the relationship between an
individual's health and having insurance coverage have proven its
positive correlation, suggesting our results may benefit from a closer
look. In assessing our dataset, as seen in Appendix 1A, we find that our
dataset contains more observations for counties with low uninsured
individuals, or equivalently, counties where most people are covered. As
the timeframe of our dataset is 2018-2022, it is likely that the
aforementioned observations require greater scrutiny of the significance
of the impact of this variable on average life expectancy of a county.~

The percentage of population with limited access to healthy foods
predictor was not statistically significant in our model, suggesting
that the effect of this environmental factor is minor or intertwined
with economic variables, such as income, rather than being a direct or
standalone influence. In terms of residential segregation, for every 1
unit increase in a county's index value (corresponding to increased
segregation), its average life expectancy increases by 0.0071 years in
the South, increases by 0.0068 years in the West, decreases by 0.0055
years in the Northeast, and decreases by 0.0004 years in the Midwest, as
seen in Figure 1. However, these regional differences are not
statistically significant at the 0.05 significance level given the high
p-values of all residential segregation-region interaction terms. We
confirmed this result with a nested F-test, comparing a full model to a
reduced model that excluded the interaction term between region and
residential segregation. This did not show a statistically significant
difference in RSS (p=0.624), indicating that the interaction between
region and residential segregation does not add meaningful explanatory
power to our model, Consequently, we did not find sufficient evidence to
support regional variations in the relationship between segregation and
life expectancy. Instead, based on residential segregation's coefficient
estimate in the model, life expectancy does appear to increase overall
with an increase in residential segregation, however minor this increase
may be. One possible theory for this observation is that counties with
more racial uniformity might experience less racial conflict and more
social cohesion, especially for minority communities.

@@

The adjusted R-squared value for the model was 0.6065, indicating that a
majority of the variability in life expectancy was explained by the
socioeconomic and racial predictors included in the model. In conducting
diagnostics on the multilinear regression model, we first checked to see
if the model met assumptions of linearity, independence, normality, and
homoscedasticity. The residuals vs.~fitted plot showed relatively equal
variance and no discernible pattern, meaning that the linearity and
homoscedasticity assumptions were reasonably met. In addition, because
each observation in the dataset represented a unique county in the U.S.,
independence could be reasonably assumed. Assessing the Q-Q Plot for
normality, the residual distribution was approximately normal, despite a
slight divergence on both tails of the plot. Cook's distance was also
assessed using the residuals vs.~leverage plot; no points were found to
be influential. There was a high leverage point (Mineral County,
Nevada), and refitting the model without this point yielded no
substantial changes in the coefficient estimates for statistically
significant predictors; however, the p-value for residential segregation
increased from 0.031 to 0.054. Finally, with a VIF \textless2 for all
predictors, there was little to no multicollinearity among the
predictors.

@@

Table 3 below displays the odds ratio results from the logistic
regression model for school funding adequacy, with the South as the
baseline category for the categorical region variable.~While all
estimates are statistically significant at the 0.05 significance level,
exponentiated regression coefficient estimates from the logistic model
demonstrate that the level of residential segregation, the median
household income, and median property tax of the county have very
minimal impacts on the odds of a school being adequately funded. This
finding is interesting as looking at Figure 2, we see that across
regions, the average racial segregation index is consistent across
school funding adequacy categories.~

Region, however, has a substantial impact on the odds of school funding
adequacy.~ Being located in the Northeast or the Midwest has the
greatest impact on how well the school is funded, with the odds of
adequate school funding being over 200 times higher in a Northeast
county compared to a Southern county, and the odds of adequate school
funding being over 3 times higher in a Northeast county compared to a
Southern county, holding all other variables constant. Such disparities
across the country are caused by a number of factors, including: (1)
capacity - how well off a state is based on its economy and resources,
and (2) effort - the states willingness to provide funding for
education. Wealthier states with a high fiscal capacity, (typically
those in the Northeast), have more funding available to spend on
education than states with more limited resources (typically those in
the South and the West).~

@@

To assess logistic regression assumptions, we first plotted each
numerical predictor against the log odds of school funding adequacy. All
plots showed a mostly linear relationship, indicating that the linearity
assumption was largely met; interestingly, different linear trends were
observed within each plot based on region, pointing to potential
interaction effects between region and the three numerical predictors.
GVIF for all predictors ranged between 1 and 3, suggesting that there
could be moderate multicollinearity between predictors, but not enough
to warrant a reconsideration of included variables. Cook's distance was
also less than 0.05 for all points, meaning that there were no highly
influential observations in the model. Evaluating our model, we found
that the logistic regression model demonstrated a strong overall
performance with an accuracy rate of 80.33\%. The model had a high
sensitivity of 91\%, indicating that it accurately predicted 91\% of
actual positive cases of adequate school funding when evaluated on our
dataset. However, it had a 60\% specificity rate, highlighting it
correctly identified cases of inadequate school funding only 60\% of the
time. Overall, looking at the ROC curve below, the AUC is 0.858,
indicating a moderately strong discriminate ability.~

@@

In our analysis, we observed the significant impact of the regional
location of a county on both its average life expectancy (a health
indicator) and school funding adequacy (an educational indicator)--two
key components of societal and an individual's well-being. Life
expectancy is highest in the Northeast, followed by the Midwest, West,
and South, while school funding adequacy is significantly greater in the
Northeast and Midwest compared to the South. Our findings highlight
substantial differences in both outcomes between regions, which are
often caused by different economic capabilities and different
allocations of resources among countries. This study provides empirical
evidence that underscores the importance for equitable social policies
and targeted investments to address regional disparities and promote
well-being across all communities.

@@

>>>>

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\usepackage{float}
\floatplacement{table}{H}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

This study examines the relationships between socioeconomic, health, and
educational indicators in U.S. counties using data from the County
Health Rankings \& Roadmaps program and IPUMS. We analyze how factors
such as residential segregation, health insurance coverage, access to
healthy foods, and region impact life expectancy, and how residential
segregation and region affect school funding adequacy. Our findings
reveal that life expectancy is influenced by residential segregation and
uninsured rates, though these effects are minor compared to the more
substantial influence of household income and regional differences. Life
expectancy averages are highest in the Northeast, followed by the
Midwest, West, and South. Region also plays the most significant role
out of all included variables in determining the likelihood of school
funding adequacy, with schools in the Northeast and Midwest being far
more likely to receive adequate funding than those in the South. Other
factors, such as residential segregation, property taxes, and household
income, show statistically significant but smaller effects. These
results highlight the complex interplay between socioeconomic variables
and geographic location in shaping public well-being. By identifying key
disparities in health and education, this study underscores the
importance of equitable resource allocation and targeted policies to
address regional and socioeconomic inequalities.

@@

Life expectancy and school funding are important indicators of public
well-being because they capture fundamental aspects of health,
education, and social equity that are essential for the development of
individuals and communities. Life expectancy is an important indicator
that reflects not only the overall health of a society, but also its
stability, economic resilience, and levels of inequality. While access
to quality healthcare and nutritious foods are drivers of well-being,
where you live and the nature of the community you live in likely also
have an influence on health outcomes such as life expectancy. According
to ``The Root Causes of Health Inequity - Communities in Action'' report
from the National Institutes of Health, we can infer that differences in
life expectancy between regions and socioeconomic groups often reveal
systemic inequalities, with marginalized communities experiencing
shorter life spans due to limited access to health care, healthy living
environments, and economic opportunities.\textsuperscript{1}~When it
comes to educational indicators, adequately funded schools ensure that
students have equal access to learning opportunities, serving as a
crucial investment in social mobility. The Stanford Center for
Opportunity Policy in Education highlights that ``the unequal allocation
and inadequate levels of resources in schools and communities {[}are{]}
at the heart of many gaps in student opportunity.''\textsuperscript{2}
This emphasizes the importance of equitable and adequate school funding
in closing opportunity gaps and empowering students from disadvantaged
backgrounds to achieve academic and economic success. By better
understanding the correlates of school funding adequacy, we can take a
major step towards implementing policy that targets the areas and
communities most affected by this issue.

@@

Variables of interest were selected \emph{a priori} based on their
perceived relevance to the two outcomes we wanted to better understand:
average life expectancy and school funding adequacy. While nutrition and
access to quality healthcare are inherently linked to general wellbeing,
it is worthwhile to assess how influential the environmental and
financial aspects of these factors are on our tangible outcome.
Therefore, we selected two key predictors for our life expectancy model:
the percentage of the population with limited access to healthy foods
and the percentage of uninsured adults in a county. The former is
defined by the US Department of Agriculture as ``the percentage of the
{[}county{]} population that is low-income and does not live close to a
grocery store'', where ``close'' is defined differently for rural and
nonrural areas.\textsuperscript{6} The latter variable represents the
percentage of adults in a county younger than 65 who lack health
insurance. We also were interested in seeing how residential segregation
would impact life expectancy among these predictors, given existing
studies on the negative health effects of segregation, and whether this
relationship would exhibit any variations across different regions. This
is why we chose to include residential segregation index values as a
predictor. The residential segregation index, used by the County Health
Rankings \& Roadmaps program, measures how evenly two groups, such as
Black and white residents, are distributed across geographic areas, with
values ranging from 0 (complete integration) to 100 (complete
segregation).\textsuperscript{7}~

@@

\subsubsection{Data Overview}\label{data-overview}

@@

Based on the multiple linear regression results, residential
segregation, percentage of uninsured adults, region, and median
household income all showed statistically significant effects on life
expectancy. Specifically, for every \$10,000 increase in median
household income, life expectancy increases by 1.25 years on average,
holding other variables constant. In addition, the impact of region on
life expectancy was substantial: life expectancy is on average 1.96
years higher in the West region compared to the South, 2.92 years higher
in the Northeast compared to the South, and 1.92 years higher in the
Midwest compared to the South, even when controlling for income,
uninsured population, and racial diversity. This suggests, income as a
factor withstanding, the differing quality of and access to healthcare
and public services found in each region can have a significant impact
on life expectancy.

Surprisingly, holding all other variables constant, for every 1 unit
increase in percentage of uninsured adults in a county, a county's
average life expectancy increases by 0.032 years. While this was
statistically significant, many studies covering the relationship
between an individual's health and having insurance coverage have proven
its positive correlation, suggesting our results may benefit from a
closer look. In assessing our dataset, as seen in Appendix A1, we find
that our dataset contains more observations for counties with low
uninsured individuals, or equivalently, counties where most people are
covered. As the timeframe of our dataset is 2018-2022, it is likely that
the aforementioned observations require greater scrutiny of the
significance of the impact of this variable on average life expectancy
of a county.~

The percentage of population with limited access to healthy foods
predictor was not statistically significant in our model, suggesting
that the effect of this environmental factor is minor or intertwined
with economic variables, such as income, rather than being a standalone
influence. In terms of residential segregation, for every 1 unit
increase in a county's index value (corresponding to increased
segregation), its average life expectancy increases by 0.0071 years in
the South, increases by 0.0068 years in the West, decreases by 0.0055
years in the Northeast, and decreases by 0.0004 years in the Midwest, as
seen in Figure 1. However, these regional differences are not
statistically significant at the 0.05 significance level given the high
p-values of all residential segregation-region interaction terms. We
confirmed this result with a nested F-test, comparing a full model to a
reduced model that excluded the interaction term between region and
residential segregation. This did not show a statistically significant
difference in RSS (\emph{p}=0.624), indicating that the interaction
between region and residential segregation does not add meaningful
explanatory power to our model, Consequently, we did not find sufficient
evidence to support regional variations in the relationship between
segregation and life expectancy. Instead, based on residential
segregation's coefficient estimate in the model, life expectancy does
appear to increase overall with an increase in residential segregation,
however minor this increase may be. One possible theory for this
observation is that counties with more racial uniformity might
experience less racial conflict and more social cohesion, especially for
minority communities, but this should be further investigated in future
studies.

@@

The adjusted R-squared value for the model was 0.6065, indicating that a
majority of the variability in life expectancy was explained by the
socioeconomic and racial predictors included in the model. In conducting
diagnostics on the multilinear regression model, we first checked to see
if the model met assumptions of linearity, independence, normality, and
homoscedasticity. The residuals vs.~fitted plot showed relatively equal
variance and no discernible pattern, meaning that the linearity and
homoscedasticity assumptions were reasonably met. In addition, because
each observation in the dataset represented a unique county in the U.S.,
independence could be reasonably assumed. Assessing the Q-Q Plot for
normality, the residual distribution was approximately normal, despite a
slight divergence on both tails of the plot. Cook's distance was also
assessed using the residuals vs.~leverage plot; no points were found to
be influential. There was a high leverage point (Mineral County,
Nevada), and refitting the model without this point yielded no
substantial changes in the coefficient estimates for statistically
significant predictors; however, the \emph{p}-value for residential
segregation increased from 0.031 to 0.054. Finally, with a VIF
\textless2 for all predictors, there was little to no multicollinearity
among the predictors.

@@

Table 3 below displays the odds ratio results from the logistic
regression model for school funding adequacy, with the South as the
baseline category for the categorical region variable. While all
estimates are statistically significant at the 0.05 significance level,
exponentiated regression coefficients from the logistic model
demonstrate that a county's median household income and median property
tax have almost no impact on the odds of its schools being adequately
funded. Our results demonstrate that a one unit increase to the
residential segregation index increases the odds of school funding
adequacy by 0.02 times, allowing us to conclude that residential
segregation has a minimal effect on the odds of the school being
adequately funded. Figure 2 demonstrates an interesting trend---each
region shows a different relationship between the residential
segregation distribution of adequately and inadequately funded
schools,~pointing to a potential interaction between region and
segregation. ~

Region has a substantial impact on the odds of school funding
adequacy.~Being located in the Northeast or the Midwest has the greatest
impact on how well a school is funded, with the odds of adequate school
funding being over 200 times higher in a Northeast county compared to a
Southern county, and the odds of adequate school funding being over 3
times higher in a Midwest county compared to a Southern county, holding
all other variables constant. Such disparities across the country are
caused by a number of factors, including: (1) capacity - how well off a
state is based on its economy and resources, and (2) effort - the
state's willingness to provide funding for education. Wealthier states
with a high fiscal capacity, (typically those in the Northeast), have
more funding available to spend on education than states with more
limited resources (typically those in the South and the West).~

@@

To assess logistic regression assumptions, we first plotted each
numerical predictor against the log odds of school funding adequacy. All
plots showed a mostly linear relationship, indicating that the linearity
assumption was largely met; interestingly, different linear trends were
observed within each plot based on region, further supporting potential
interaction effects between region and the three numerical predictors.
GVIF for all predictors ranged between 1 and 3, suggesting that there
could be moderate multicollinearity between predictors, but not enough
to warrant a reconsideration of included variables. Cook's distance was
also less than 0.05 for all points, meaning that there were no highly
influential observations in the model. Evaluating our model, we found
that the logistic regression model demonstrated a strong overall
performance with an accuracy rate of 80.33\%. The model had a high
sensitivity of 91\%, indicating that it accurately predicted 91\% of
actual positive cases of adequate school funding when evaluated on our
dataset. However, it had a 60\% specificity rate, highlighting it
correctly identified cases of inadequate school funding only 60\% of the
time. Overall, looking at the ROC curve below, the AUC is 0.858,
indicating a moderately strong discriminate ability.~

@@

In our analysis, we observed the significant impact of the regional
location of a county on both its average life expectancy (a health
indicator) and school funding adequacy (an educational indicator)--two
key components of societal and individual well-being. Life expectancy is
highest in the Northeast, followed by the Midwest, West, and South,
while school funding adequacy is significantly greater in the Northeast
and Midwest compared to the South. Our findings highlight substantial
differences in both outcomes between regions, which are often caused by
different economic capabilities and different allocations of resources
among countries. This study provides empirical evidence that underscores
the importance for equitable social policies and targeted investments to
address regional disparities and promote well-being across all
communities.

@@

\subsection{\texorpdfstring{\protect\includegraphics{images/clipboard-2912764107.png}}{}}\label{section}
